Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex

>>>>

\subsection{Use of Data Integration Features}

To determine whether participants used the data integration features of DP, we looked at use of the \emph{multipath selection} and \emph{Same-As} features of the system.   Pertaining to path selection, all participants readily used the path selection process to select values.   Five participants (25\%) deliberately used multipath selection, defined as selecting more than one active path per group at the same time to display common values across heterogeneous items. (We did not count accidental use of multipath, such as happened a few times when a participant had an already active path and wanted to switch to a separate path accidentally).

Participants used the drag-and-drop \emph{Same-As} capability extensively. Sixteen (80\%) used \emph{Same-As} as least once; among these participants, they used \emph{Same-As} an average of 4.6 times per trial. We counted a single ``use'' as a single drag-and-drop of an individual item, or a drag-and-drop operation of an entire group onto another.  (We did not differentiate enumerated value consolidation from entity consolidation, as these operations were not discernably different from the interface perspective.)

\subsection{Use of Visualisation Features}

To determine to what extent visualisation tools were used in condition A, 13 (65\%) used charting tools at least once, while 15 (75\%) used the map.  Determining the impact these had on performance, we performed a multiple regression on time taken with the number of uses of charting and mapping as variables.   We found significant effects of both charting and mapping variables on time taken, ($R^2_{adj} = 0.04; F(2,17)=3.79; p<0.05$), with coefficients ($Y_0=8.91;\beta_{charts}=0.49;\beta_{maps}=-1.05$) demonstrating that charting positively influenced time taken, while the use of maps led to shorter times.
